Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-05-04 hb.tex
remove _f from factory ops

  Fact mul0r : left_zero zero mul_f.
  Proof.
  move=> x; rewrite -[LHS]add0r addrC.
  rewrite -{2}(addNr (mul_f x x)) (addrC (opp _)) addrA.
  by rewrite -mulrDl_f add0r addrC addNr.
  Qed.

  Fact mulr0 : right_zero zero mul_f.
  Proof.
  move=> x; rewrite -[LHS]add0r addrC.
  rewrite -{2}(addNr (mul_f x x)) (addrC (opp _)) addrA.
  by rewrite -mulrDr_f add0r addrC addNr.
  Qed.

  Definition to_SemiRing_of_Monoid := SemiRing_of_Monoid.Build A _ mul_f mulrA_f
     mul1r_f mulr1_f mulrDl_f mulrDr_f mul0r mulr0.
  HB.instance A to_SemiRing_of_Monoid.

@@

  Lemma addrC : commutative (add : A -> A -> A).
  Proof.
  have innerC (a b : A) : a + b + (a + b) = a + a + (b + b).
    by rewrite -[a+b]mul1r_f -mulrDl_f mulrDr_f !mulrDl_f !mul1r_f.
  have addKl (a b c : A) : a + b = a + c -> b = c.
    apply: can_inj (add a) (add (opp_f a)) _ _ _.
    by move=> x; rewrite addrA addNr_f add0r.
  have addKr (a b c : A) : b + a = c + a -> b = c.
    apply: can_inj (add ^~ a) (add ^~ (opp_f a)) _ _ _.
    by move=> x; rewrite /= -addrA addrN_f addr0.
  move=> x y; apply: addKl (x) _ _ _; apply: addKr (y) _ _ _.
  by rewrite -!addrA [in RHS]addrA innerC !addrA.
  Qed.

  (* Builder to the bottom right mixin. *)
  Definition to_AbelianGroup_of_Monoid :=
    AbelianGroup_of_Monoid.Build A opp_f addrC addNr_f.
  HB.instance A to_AbelianGroup_of_Monoid.

  (* Builder to the top right factory, which is compiled to the bottom left mixin. *)
  Definition to_Ring_of_AbelianGroup := Ring_of_AbelianGroup.Build A one_f mul_f
    mulrA_f mul1r_f mulr1_f mulrDl_f mulrDr_f.
  HB.instance A to_Ring_of_AbelianGroup.

>>>>

  Fact mul0r : left_zero zero mul.
  Proof.
  move=> x; rewrite -[LHS]add0r addrC.
  rewrite -{2}(addNr (mul x x)) (addrC (opp _)) addrA.
  by rewrite -mulrDl add0r addrC addNr.
  Qed.

  Fact mulr0 : right_zero zero mul.
  Proof.
  move=> x; rewrite -[LHS]add0r addrC.
  rewrite -{2}(addNr (mul x x)) (addrC (opp _)) addrA.
  by rewrite -mulrDr add0r addrC addNr.
  Qed.

  Definition to_SemiRing_of_Monoid := SemiRing_of_Monoid.Build A _ mul mulrA
     mul1r mulr1 mulrDl mulrDr mul0r mulr0.
  HB.instance A to_SemiRing_of_Monoid.

@@

  Lemma addrC : commutative (add : A -> A -> A).
  Proof.
  have innerC (a b : A) : a + b + (a + b) = a + a + (b + b).
    by rewrite -[a+b]mul1r -mulrDl mulrDr !mulrDl !mul1r.
  have addKl (a b c : A) : a + b = a + c -> b = c.
    apply: can_inj (add a) (add (opp a)) _ _ _.
    by move=> x; rewrite addrA addNr add0r.
  have addKr (a b c : A) : b + a = c + a -> b = c.
    apply: can_inj (add ^~ a) (add ^~ (opp a)) _ _ _.
    by move=> x; rewrite /= -addrA addrN addr0.
  move=> x y; apply: addKl (x) _ _ _; apply: addKr (y) _ _ _.
  by rewrite -!addrA [in RHS]addrA innerC !addrA.
  Qed.

  (* Builder to the bottom right mixin. *)
  Definition to_AbelianGroup_of_Monoid :=
    AbelianGroup_of_Monoid.Build A opp addrC addNr.
  HB.instance A to_AbelianGroup_of_Monoid.

  (* Builder to the top right factory, which is compiled to the bottom left mixin. *)
  Definition to_Ring_of_AbelianGroup := Ring_of_AbelianGroup.Build A one mul
    mulrA mul1r mulr1 mulrDl mulrDr.
  HB.instance A to_Ring_of_AbelianGroup.
